\documentclass[10pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\large\bf}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}


% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
\lfoot{
\cfoot{\scriptsize  Nan-Hung Hsieh - CV - Created by R Markdown }}
\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Nan-Hung Hsieh:  CV (Curriculum Vitae)},
            pdfauthor={Nan-Hung Hsieh},
            pdfkeywords={RMarkdown, academic CV, template},
            colorlinks=true,
            linkcolor=blue,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Nan-Hung Hsieh}

\vspace{2 mm}

\hrule

\vspace{2 mm}

\moveleft.5\hoffset\centerline{Postdoctoral Research Associate, Texas A\&M University}

\moveleft.5\hoffset\centerline{ \faEnvelopeO \hspace{1 mm} \href{mailto:}{\tt \href{mailto:nhsieh@cvm.tamu.edu}{\nolinkurl{nhsieh@cvm.tamu.edu}}} \hspace{1 mm}  \faGithub \hspace{1 mm} \href{http://github.com/nanhung}{\tt nanhung} \hspace{1 mm}    \faGlobe \hspace{1 mm} \href{http://nanhung.me}{\tt nanhung.me}    | \emph{Updated:} \today}

\vspace{2 mm}

\hrule


\section{EXPERIENCE}\label{experience}

Department of Veterinary Integrative Biosciences, Texas A\&M
University\\
Postdoctoral Research Associate \hfill 08/2016 --

\hfill Supervisor: Prof.
\href{http://vetmed.tamu.edu/vibs/directorydetail?userid=13388}{Weihsueh
A. Chiu}

Division of Occupational Hazards Assessment, Institute of Labor,
Occupational Safety and Health\\
Research Associate \hfill 08/2013 -- 07/2016

\section{EDUCATION}\label{education}

Ph.D.~Bioenvironmental Systems Engineering, National Taiwan University,
2013

\begin{quote}
Dissertation: \emph{Dynamic modeling and analysis of air
pollution-associated lung function exacerbations risk}
\end{quote}

\hfill Advisor: Prof.
\href{http://homepage.ntu.edu.tw/~cmliao/}{Chung-Min Liao}

M.Eng. Bioenvironmental Systems Engineering, National Taiwan University,
2010\\
B.Sc. Safety, Health and Environmental Engineering, National United
University, 2007

\section{RESEARCH PROJECT}\label{research-project}

\textbf{Postdoctoral Research Associate} \hfill 09/2016--

\begin{quote}
U.S. Food and Drug Administration. \emph{Enhancing the reliability,
efficiency, and usability of Bayesian population PBPK modeling - Create,
implement, and evaluate a robust Global Sensitivity Analysis algorithm
to reduce PBPK model parameter dimensionality}. 1U01FD005838-01.
\end{quote}

\textbf{Principle Investigator} \hfill 03/2015--12/2015

\begin{quote}
Institute of Labor, Occupational Safety and Health. \emph{Assessing the
Fine Particles-Associated Exposure Hazards for Workers in Workplace}.
ILOSH104-A310.
\end{quote}

\textbf{Principle Investigator} \hfill 03/2014--12/2014

\begin{quote}
Institute of Labor, Occupational Safety and Health. \emph{Assessing
Health Risks for Workers in High Lead Exposed Factories}. ILOSH103-A307.
\end{quote}

\section{AWARDS}\label{awards}

\begin{itemize}
\tightlist
\item
  Outstanding R\&D alternative military award, Taiwan Ministry of the
  Interior, 2016
\item
  Outstanding Alumni, National United University, 2015
\item
  Best PhD Academic Research Paper, National Taiwan University, 2012
\end{itemize}

\section{SERVICES TO THE PROFESSION}\label{services-to-the-profession}

\subsection{Editorial Board Member}\label{editorial-board-member}

\begin{quote}
\emph{Journal of Environment Pollution and Human Health}
\end{quote}

\subsection{Peer review for scientific
journals}\label{peer-review-for-scientific-journals}

\begin{itemize}
\tightlist
\item
  Computational and Mathematical Methods in Medicine (6)
\item
  Environmental Research (1)
\item
  International Journal of Environmental Research and Public Health (4)
\item
  International Journal of Molecular Sciences (1)
\item
  International Journal of Occupational and Environmental Health (1)
\item
  Science of the Total Environment (1)
\item
  Stochastic Environmental Research and Risk Assessment (1)
\end{itemize}

\section{COMPUTER INTERESTS}\label{computer-interests}

\begin{itemize}
\tightlist
\item
  Operating System: GNU/Linux
\item
  Scientific computing: C, R, Python, GNU/MCSim
\item
  Other: Git, High-Performance Computer, HTML + CSS
\end{itemize}

\section{OTHER}\label{other}

\begin{itemize}
\tightlist
\item
  Membership: Society of Toxicology (USA)
\item
  Language: Mandarin (Native), English
\item
  Personal Interests: Computer \& Information Technology
\end{itemize}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\section{PUBLICATIONS}\label{publications}

\subsection{Journal Article}\label{journal-article}

2018

\begin{quote}
Grimm FA, Blanchette A, House JS, Ferguson K, \textbf{Hsieh NH},
Dalaijamts C, Wrigt AA, Anson B, Wright FA, Chiu WA, Rusyn I*. 2018. A
human population-based organotypic \emph{in vitro} model for
cardiotoxicity screening. ALTEX. In Press.
\end{quote}

\begin{quote}
Cheng YH, Lin YJ, Chen SC*, You SH, Chen WY, \textbf{Hsieh NH}, Yang YF,
Liao CM*. 2018. Assessing health burden risk and control effect on
dengue fever infection in southern region of Taiwan. Infection and Drug
Resistance. In Press.
\end{quote}

\begin{quote}
Luo YS, \textbf{Hsieh NH}, Chiu WA, Rusyn I*. Comparative analysis of
metabolism of trichloroethylene and tetrachloroethylene among tissues
and mouse strains. Toxicology 2018 Nov; 409(1): 33-43.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Reisfeld B, Bois FY, Chiu WA*. Applying a global
sensitivity analysis workflow to improve the computational efficiencies
in physiologically-based pharmacokinetic modeling. Frontiers in
Pharmacology 2018 Jun; 9:588.
\end{quote}

\begin{quote}
Cheng YH, Chou WC, Yang YF, Huang CW, How CM, Chen SC, Chen WY,
\textbf{Hsieh NH}, Lin YJ, You SH, Liao CM*. PBPK/PD assessment for
Parkinson's disease risk posed by airborne pesticide paraguat exposure.
Environmental Science and Pollution Research 2018 Feb; 25(6):5359-68.
\end{quote}

2017

\begin{quote}
\textbf{Hsieh NH}, Lin YJ, Yang YF, Liao CM*. Assessing the
oseltamivir-induced resistance risk and implications for influenza
infection control strategies. Infection and Drug Resistance 2017 Jul;
10: 215-26.
\end{quote}

\begin{quote}
Cheng YH, You SH, Lin YJ, Chen SC, Chen WY, Chou WC, \textbf{Hsieh NH},
Liao CM*. Mathematical modeling of postcoinfection with influenza A
virus and Streptococcus pneumoniae, with implications for pneumonia and
COPD-risk assessment. International Journal of Chronic Obstructive
Pulmonary Disease 2017 Jul; 12:1973-88.
\end{quote}

\begin{quote}
Lin YJ, Ling MP*, Chen SC, Chen WY, \textbf{Hsieh NH}, Cheng YH, You SH,
Chou WC, Lin MC, Liao CM*. 2017. Mixture risk assessment due to
ingestion of arsenic, copper, and zinc from milkfish farmed in
contaminated coastal areas. Environmental Science and Pollution
Research: Jun; 24(17):14616-26.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Chung SH, Chen SC, Chen WY, Cheng YH, Lin YJ, You SH,
Liao CM*. Anemia risk in relation to lead exposure in lead-related
manufacturing. BMC Public Health 2017 May; 17:389.
\end{quote}

2016

\begin{quote}
Chen WY*, Chen ZY, \textbf{Hsieh NH}, Ju YT. Site-specific water quality
criteria for lethal/sublethal protections of freshwater fish exposed to
zinc in southern Taiwan. Chemosphere 2016 Sep; 159:412-9.
\end{quote}

\begin{quote}
Cheng YH, Wang CH, You SH, \textbf{Hsieh NH}, Chen WY, Chio CP, Liao
CM*. Assessing coughing-induced influenza droplet transmission and
implications for infection risk control. Epidemiology and Infection 2016
Jan; 144(2):333-45.
\end{quote}

2015

\begin{quote}
Chen WY, Cheng YH, \textbf{Hsieh NH}, Wu BC, Chou WC, Ho CC, Chen JK,
Liao CM*, Lin P*. Physiologically-based pharmacokinetic modeling of zinc
oxide nanoparticles and zinc nitrate in mice. International Journal of
Nanomedicine 2015 Oct; 10:6277-6292.
\end{quote}

\begin{quote}
Liao CM*, Wu BC, Cheng YH, You SH, Lin YJ, \textbf{Hsieh NH}. Ceramics
manufacturing contributes to ambient silica air pollution and burden of
lung disease. Environmental Science and Pollution Research 2015 Oct;
22(19):15067-79.
\end{quote}

\begin{quote}
Chen SC, \textbf{Hsieh NH}, You SH, Wang CH, Liao CM*. 2015. Behavioural
response in educated young adults towards influenza A(H1N1)pdm09.
Epidemiology and Infection 2015 Jul; 143(9):1846-57.
\end{quote}

\begin{quote}
Liao CM*, Huang TL, Cheng YH, Chen WY, \textbf{Hsieh NH}, Chen SC, Chio
CP. Assessing dengue infection risk in southern region of Taiwan and
implications for control. Epidemiology and Infection 2015 Apr;
143(5):1059-72.
\end{quote}

\begin{quote}
Liao CM*, Huang TL, Lin YJ, You SH, Cheng YH, \textbf{Hsieh NH}, Chen
WY. Regional response of dengue fever epidemics to interannual variation
and related climate variability. Stochastic Environmental Research and
Risk Assessment 2015 Mar; 29(3):947-58.
\end{quote}

2014

\begin{quote}
\textbf{Hsieh NH}, Cheng YH, Liao CM*. Changing variance and skewness as
leading indicators for detecting ozone exposure-associated lung function
decrement. Stochastic Environmental Research and Risk Assessment 2014
Dec; 28(8):2205-16.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Liao CM*. In vitro measurement and dynamic
modeling-based approaches for deposition risk assessment of inhaled
aerosols in human respiratory system. Atmospheric Environment 2014 Oct;
95:268-76.
\end{quote}

2013

\begin{quote}
\textbf{Hsieh NH}, Liao CM*. Fluctuations in air pollution give risk
warning signals of asthma hospitalization. Atmospheric Environment 2013
Aug; 75:206--16.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Liao CM*. Assessing exposure risk for dust storm
events-associated lung function decrement in asthmatics and implications
for control. Atmospheric Environment 2013 Apr; 68:256--64.
\end{quote}

2012

\begin{quote}
Liao CM*, Cheng YH, Lin YJ, \textbf{Hsieh NH}, Huang TL, Chio CP, Chen
SC, Ling MP. A Probabilistic transmission and population dynamic model
to assess tuberculosis infection risk. Risk Analysis 2012 Aug; 32(8):
1420--32.
\end{quote}

\begin{quote}
Chio CP, Chen WY, Chou WC, \textbf{Hsieh NH}, Ling MP, Liao CM*.
Assessing the potential risk to zebrafish posed by environmentally
copper and silver nanoparticles. Science of the Total Environment 2012
Mar; 420: 111--8.
\end{quote}

\begin{quote}
Liao CM*, \textbf{Hsieh NH}, Huang TL, Cheng YH, Lin YJ, Chio CP, Chen
SC, Ling MP. Assessing trends and predictors of tuberculosis in Taiwan.
BMC Public Health 2012 Jan; 12:29.
\end{quote}

2011

\begin{quote}
Liao CM*, \textbf{Hsieh NH}, Chio CP. Fluctuation analysis-based risk
assessment for respiratory virus activity and air pollution associated
asthma incidence. Science of the Total Environment 2011 Aug; 409:
3325--33.
\end{quote}

\begin{quote}
Liao CM*, Chio CP, Cheng YH, \textbf{Hsieh NH}, Chen WY, Chen SC.
Quantitative links between arsenic exposure and influenza A (H1N1)
infection-associated lung function exacerbations risk. Risk Analysis
2011 Aug; 31(8): 1281--94.
\end{quote}

\begin{quote}
Ling MP, Chio CP, Chou WC, Chen WY, \textbf{Hsieh NH}, Lin YJ, Liao CM*.
Assessing the potential exposure risk and control for airborne titanium
dioxide and carbon black nanoparticles in the workplace. Environmental
Science and Pollution Research 2011 Jul; 18(6): 877--89.
\end{quote}

2010

\begin{quote}
Liao CM*, \textbf{Hsieh NH}, Chio CP, Chen SC. Assessing the
exacerbations risk of influenza-associated chronic occupational asthma.
Risk Analysis 2010 Jul; 30(7): 1062--75.
\end{quote}

\begin{quote}
Liao CM*, Lin TL, \textbf{Hsieh NH}, Chen WY. Assessing the
arsenic-contaminated rice (Oryza sativa) associated children skin
lesions. Journal of Hazardous Materials 2010 Apr; 176(1--3): 239--51.
\end{quote}

\subsection{Conference Papers}\label{conference-papers}

\begin{quote}
\textbf{Hsieh NH}, Reisfeld B, Bois FY, Chiu WA. Applying a global
sensitivity analysis workflow to improve computational efficiencies in
physiologically-based pharmacokinetic model. 57th SOT Annual Meeting,
San Antonio, USA, March 11-15, 2018.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Reisfeld B, Bois FY, Chiu WA. Applying A Global
Sensitivity Analysis Workflow to Improve Computational Efficiency in
Physiologically-Based Pharmacokinetic Modeling. 2017 SRA Annual Meeting,
Arlington, USA, December 10-14, 2017.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Chung SH. Meta-Analysis of the Fine Particulate
Matters-Associated Occupational Health Risks. SOT 56th Annual Meeting,
Baltimore, USA, March 12--16, 2017.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Liao CM. Modeling honey bee extinction risk by
neonicotinoid insecticide (imidacloprid) exposure. SETAC Europe 26th
Annual Meeting, Nantes, France, May 22--26, 2016.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Liao CM. Fluctuating air pollution-associated asthma
incidence in Taiwan. SETAC Europe 23rd Annual Meeting, Glasgow, UK, May
12--16, 2013.
\end{quote}

\begin{quote}
\textbf{Hsieh NH}, Chio CP, Liao CM. Assessing the risks for aquatic
organisms posed by waterborne copper and silver nanoparticles. SETAC
Europe 21st Annual Meeting Milan, Italy, May 15--19, 2011.
\end{quote}

\end{document}
